---
title: "Notes on DeclareDesign *designers*"
author: "Markus Konrad"
date: "July 29, 2019"
output: html_document
---

This document is a set of notes about DeclareDesign and the *designers* in its DesignLibrary package from a DDWizard development perspective.


```{r, message=FALSE}
library(DeclareDesign)
packageVersion('DeclareDesign')
```

```{r}
library(DesignLibrary)
packageVersion('DesignLibrary')
```

## Designers

*Designers* are parametric "templates" for specific *designs*. So the the distinction between design*er* and design is important. The latter is a specific instance of a designer given a set of parameters.

A designer is a function, e.g. the `two_arm_designer`:

```{r}
class(two_arm_designer)
```

It has some attributes that provide meta-data for the designer:

```{r}
attributes(two_arm_designer)
```

```{r}
attr(two_arm_designer, 'description')
```

These attributes are important for DDWizard. For example, the `definitions` attribute specifies the designer's arguments, their type, range and whether they except a vector as input. These metadata are an addition to what is returned by `formals()` as explained in the next section.

### Designer parameters

You can get a designer's arguments and their default values as list with `formals()`:

```{r}
formals(two_arm_designer)
```

As you can see, parameters can also accept R syntax (like the default values for `treatment_mean` and `control_sd`) which is evaluated inside the designer function.


## A specific design instance

Calling a designer function with some specific parameters generates a specific design instance:

```{r}
two_arm_N10 <- two_arm_designer(N = 10)
two_arm_N10
```

This instance contains all the steps of the designer, but with specific parameters set. It's a special list of classes "design" and "dd":

```{r}
class(two_arm_N10)
```

```{r}
typeof(two_arm_N10)
```

All steps can be accessed by name:

```{r}
names(two_arm_N10)
```

```{r}
two_arm_N10$population
```

Generate a random population with the parameters specified by the designer:

```{r}
two_arm_N10$population()
```


Parameters cannot be changed here any more:

```{r, eval=FALSE}
two_arm_N10$population(N = 20)
## Error in two_arm_N10$population(N = 20) : unused argument (N = 20)
```

There are more attributes to the design instance:

```{r}
attributes(two_arm_N10)
```

Attribute "code" reproduces the design instance:

```{r}
attr(two_arm_N10, 'code')
```

