---
title: "Notes on DeclareDesign"
author: "Markus Konrad"
date: "October 5, 2018"
output: html_document
---

```{r}
library(DesignLibrary)
```


## A parametric design/designer object

A design object is a closure function. Sometimes it's also called "design*er*" instead of design, since it's a parametric template for a specific design.

```{r}
class(simple_two_arm_designer)
```

```{r}
typeof(simple_two_arm_designer)
```


It has some attributes that provide meta-data:

```{r}
attributes(simple_two_arm_designer)
```

```{r}
attr(simple_two_arm_designer, 'description')
```

### Designer parameters

Get a designer's arguments as list with `formals()`:

```{r}
formals(simple_two_arm_designer)
```

Parameters can be:

- numeric
- integer
- "language": a parameter dependend on some other parameter(s) (like `treatment_mean`)
- more?

## A specific design instance

Calling a designer object with some specific parameters generates a specific design instance:

```{r}
two_arm_N10 <- simple_two_arm_designer(N=10)
two_arm_N10
```

This instance contains all the steps of the designer, but with specific parameters set. It's a special list of classes "design" and "dd":

```{r}
class(two_arm_N10)
```

```{r}
typeof(two_arm_N10)
```

All steps can be accessed by name:

```{r}
names(two_arm_N10)
```

```{r}
two_arm_N10$population
```

Generate a random population with the parameters specified by the designer:

```{r}
two_arm_N10$population()
```


Parameters cannot be changed here any more:

```{r, eval=FALSE}
two_arm_N10$population(N = 20)
## Error in two_arm_N10$population(N = 20) : unused argument (N = 20)
```

There are more attributes to the design instance:

```{r}
attributes(two_arm_N10)
```

Attribute "code" reproduces the design instance:

```{r}
attr(two_arm_N10, 'code')
```

